---
title: "Links"
---
  
```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
```

## Websites

* Getting Started with R and RStudio, [view the website](https://ourcodingclub.github.io/tutorials/intro-to-r/).

* Tidy Tuesday data repository, [view the website](https://github.com/rfordatascience/tidytuesday/tree/master).

* From Data to Viz website on visualizing data,  [view the website](https://www.data-to-viz.com/#explore).

* [Julia Silge's](https://juliasilge.com/) blog posts (mostly) on TidyTuesday data analyses, [view the website](https://juliasilge.com/blog/).

## Texts

* Deep Learning and Scientific Computing with R torch, [view the free online version of the text](https://skeydan.github.io/Deep-Learning-and-Scientific-Computing-with-R-torch/).


## Videos

*  Getting started with Quarto YouTube video, [watch video on YouTube](https://youtu.be/YK6IjJkjkiI).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="_f3latmOhew",height=450) %>%
  vembedr::use_align("center")
```

*  Datasheets for Datasets video, [watch the video on YouTube](https://youtu.be/R7s7_T4yXak).
  
```{r}
#| echo: false

vembedr::embed_youtube(id="R7s7_T4yXak",height=450) %>%
  vembedr::use_align("center")
```

* Exploratory data analysis worked example video by Hadley Wickham, [watch the video on YouTube](https://youtu.be/go5Au01Jrvs).

```{r}
#| echo: false

vembedr::embed_youtube(id="go5Au01Jrvs",height=450) %>%
  vembedr::use_align("center")
```

