---
title: "Syllabus"
license: "CC BY-NC-SA 4.0"
---

```{r}
#| label: package-loads
#| include: false
#| message: false
library(kableExtra)
```

# DS 362 Data-Driven Knowledge Discovery


# Instructor Information

* **Instructor:** Dr. Jason M. Graham

* **Office:** LSC 319A 
    + **Office Hours:** TBD You may also make an appointment to meet with me outside of scheduled office hours. Appointments are not necessary for regularly scheduled office hours.

* **Email:** <jason.graham@scranton.edu>

* **Phone:** (570) 941-7491

* **Course Page:** [link](https://knowledge-discovery.netlify.app/)

# Course Materials

## Required Readings

* An Introduction to Statistical Learning 2nd Ed. by James, Witten, Hastie, and Tibshirani, freely available online [here](https://www.statlearning.com/).

* Statistical Learning with Math and R by Joe Suzuki, available online through the Weinberg Library [here](https://link-springer-com.ezp.scranton.edu/book/10.1007/978-981-15-7568-6).

* Tidy Modeling with R by
Max Kuhn & Julia Silge, freely available online [here](https://www.tmwr.org/).

## Recommended Readings

* Telling Stories with Data by Rohan Alexander, freely available online [here](https://tellingstorieswithdata.com/).

* Data Science: A First Introduction by Tiffany Timbers, Trevor Campbell, and Melissa Lee, freely available online [here](https://datasciencebook.ca/).

* Tree-Based Methods for Statistical Learning by Brandon M. Greenwell, freely available online [here](https://bgreenwell.github.io/treebook/).

* Statistical Learning from a Regression Perspective by Richard A. Berk, available online through the Weinberg Library [here](https://link-springer-com.ezp.scranton.edu/book/10.1007/978-3-030-40189-4).

## Further Reading

* Elements of Statistical Learning 2nd Ed. by Hastie, Tibshirani, and Friedman, freely available online [here](https://hastie.su.domains/ElemStatLearn/).


## R References

* Hands-On Programming with R by Garrett Grolemund, freely available online [here](https://rstudio-education.github.io/hopr/).

* R for Data Science by Hadley Wickham & Garrett Grolemund, freely available online [here](https://r4ds.had.co.nz/index.html).

*  Data Visualization A Practical Introduction by Healy, freely available online [here](https://socviz.co/index.html#preface).

# Course Information

## Course Description


### Prerequisites

## Student Learning Objectives and Assessment:

```{r}
#| include: false


course_slo <- c("After completing this course, students will be able to import, format, and transform common data-set types programmatically and build effective visualizations of data","After completing this course, students will be able to apply appropriate exploration and modeling techniques to learn from data.","After completing this course, students will be able to present and communicate results obtained via data analysis in an effective manner.")
ge_objectives <- c("All students will identify and read important texts, placing them both in historical and conceptual contexts, and write analyses and arguments pertaining to these texts.","All students will apply technological and philosophical insights to issues of science and technolo","All students will apply technological and philosophical insights to issues of science and technology in the 20th century. ")
assessment <- c("Homework, Data Package Assignment, and Project","Homework and Project","Homework, Data Package Assignment, and Project")
slos_assess <- tibble::tibble("Course SLO"=course_slo,"Assessment"=assessment)
```


```{r}
#| label: tbl-objectives
#| tbl-cap: Course objectives and assessment.
#| echo: false


kbl(slos_assess) %>%
  kable_paper(c("hover","responsive"),full_width = F) %>%
  column_spec(1, width = "25em") %>%
  column_spec(2, width = "25em")
```

# Course Policies and Procedures




##  Grading

### Grade Policy


### Grade Scale

```{r}
#| include: false
#| echo: false

grade_values <- c("94-100","90-93","87-89","83-86","80-82","76-79","72-75","69-71","65-68","60-64","<60")
grade_letters <- c("A","A-","B+","B","B-","C+","C","C-","D+","D","F")
grades_df <- tibble::tibble("Grade Range"=grade_values,"Letter Grade"=grade_letters)
```

Letter grades will be assigned based on the following scale:

```{r}
#| label: tbl-grades
#| tbl-cap: Letter grade scale.
#| echo: false
kbl(grades_df) %>%
  kable_paper(c("hover","responsive"),full_width=FALSE) 
```


# Assignments

# Course Timeline

## Weekly Schedule

 - Week 1:  
 
 - Week 2:  
 
 - Week 3: 
 
 - Week 4: 
 
 - Week 5: 
 
 - Week 6: 
 
 - Week 7: 
 
 - Week 8: 
 
 - Week 9: 
 
 - Week 10: 
 
 - Week 11: 
 
 - Week 12: 
 
 - Week 13: 
 
 - Week 14: 
 
 - Week 15: 

## Important Dates

```{r}
#| include: false
#| echo: false


events <- c("Classes begin","Drop (no grade)","Fall break","Mid-semester","Thanksgiving break","Last week","Finals")
event_date <- c(" "," "," "," "," "," "," ")
important_dates_df <- tibble::tibble("Event"=events,"Date"=event_date)
```


```{r}
#| echo: false
#| label: tbl-dates
#| tbl-cap: Important dates.

kbl(important_dates_df) %>%
  kable_paper(c("hover","responsive"),full_width = F) %>%
  column_spec(1, width = "30em",border_left=TRUE,border_right=TRUE) %>%
  column_spec(2, width = "30em",border_right=TRUE)
```


# University Resources for Students and Academic Honesty

## Students with Disabilities

Reasonable academic accommodations may be provided to students who submit relevant and current documentation of their disability.  Students are encouraged to contact the Center for Teaching and Learning Excellence (CTLE) at <disabilityservices@scranton.edu> or (570) 941-4038 if they have or think they may have a disability and wish to determine eligibility for any accommodations.  For more information, please visit <http://www.scranton.edu/disabilities>. 

## Writing Center Services

The Writing Center focuses on helping students become better writers.  Consultants will work one-on-one with students to discuss students’ work and provide feedback at any stage of the writing process.  Scheduling appointments early in the writing progress is encouraged.

To meet with a writing consultant, call (570) 941-6147 to schedule an appointment, or send an email with your available meeting times, the course for which you need assistance, and your phone number to: <writing-center@scranton.edu>. The Writing Center does offer online appointments for our distance learning students. 

## Academic Honesty and Integrity

Each student is expected to do their own work. It is also expected that each student respect and abide by the Academic Code of Honesty as set forth in the University of Scranton student handbook. Conduct that violates the Academic Code of Honesty includes plagiarism, duplicate submission of the same work, collusion, providing false information, unauthorized use of computers, theft and destruction of property, and unauthorized possession of tests and other materials. Steps taken in response to suspected violations may include a discussion with the instructor, an informal meeting with the dean of the college, and a hearing before the Academic Dishonesty Hearing Board. Students  who are found to have violated the Code will ordinarily be assigned the grade F by the instructor and may face other sanctions. The complete Academic Code of Honesty is located on the University website at <https://www.scranton.edu/academics/wml/acad-integ/acad-code-honesty.shtml>. 

## My Reporting Obligation as a Responsible Employee

As a faculty member, I am deeply invested in the well-being of each student I teach. I am here to assist you with your work in this course. Additionally, if you come to me with other non-course-related concerns, I will do my best to help. It is important for you to know that all faculty members are required to report incidents of sexual harassment or sexual misconduct involving students. This means that I cannot keep information about sexual harassment, sexual assault, sexual exploitation, intimate partner violence or stalking confidential if you share that information with me. I will keep the information as private as I can but am required to bring it to the attention of the University’s Title IX Coordinator, Elizabeth M. Garcia, or Deputy Title IX Coordinator, Diana M. Collins, who, in conversation with you, will explain available support, resources, and options. I will not report anything to anybody without first letting you know and discussing choices as to how to proceed. The University’s Counseling Center (570-941-7620) is available to you as a confidential resource; counselors (in the counseling center) do not have an obligation to report to the Title IX Coordinator.

## Non-discrimination Statement

The University is committed to providing an educational, residential, and working environment that is free from harassment and discrimination. Members of the University community, applicants for employment or admissions, guests, and visitors have the right to be free from harassment or discrimination based on race, color, religion, ancestry, gender, sex, pregnancy, sexual orientation, gender identity or expression, age, disability, genetic information, national origin, veteran status, or any other status protected by applicable law.

Students who believe they have been subject to harassment or discrimination based on any of the above class of characteristics, or experience sexual harassment, sexual misconduct or gender discrimination should contact Elizabeth M. Garcia, Title IX Coordinator, (570) 941-6645 <elizabeth.garcia2@scranton.edu>, Deputy Title IX Coordinators Diana M. Collins (570) 941-6645 <diana.collins@scranton.edu>, or Ms. Lauren Rivera, AVP for Student Life and Dean of Students, at (570)941-7680 <lauren.rivera@scranton.edu>. The United States Department of Education’s Office for Civil Rights (OCR) enforces Title IX. Information regarding OCR may be found at <www.ed.gov/about/offices/list/ocr/index.html>     

The University of Scranton Sexual Harassment and Sexual Misconduct Policy can be found online at <https://www.scranton.edu/diversity>. All reporting options and resources are available at <https://www.scranton.edu/CARE>. 

### About Pronouns

It is easy to make assumptions about an individual's pronouns, but we try not to! Please tell us in class or via a private email if you would like to let us know what your pronouns are, if/when you would like us (and others) to use them, and certainly feel free to correct us or others if we make a mistake. Using the pronouns that a person has indicated they prefer is considered both professional and polite, and as such we ask that all members of our class use the appropriate pronouns.

If you have questions about this, please feel free to look up more information here (<https://www.mypronouns.org/>) or email <jason.graham@scranton.edu> with any questions.

## Student Mental Health: Suggestions and Resources

Many students experience mental health challenges at some point in college. Struggles vary and might be related to academics, anxiety, depression, relationships, grief/loss, substance abuse, and other challenges. There are resources to help you and getting help is the smart and courageous thing to do.

* Counseling Center (6th Floor O’Hara Hall; 570-941-7620) – Free, confidential individual and group counseling is available on campus.

* Teletherapy – For students who wish to access therapy via video, phone, and/or chat, the University offers a teletherapy resource. Please contact the Counseling Center (570-941-7620) to inquire about teletherapy.

*   [Mental Health Screenings](https://www.scranton.edu/studentlife/studentaffairs/chew/mental-health-screenings-.shtml) – Confidential, online “check up from your neck up” to help you determine if you should connect with a mental health professional.

* Dean of Students Office (201 DeNaples Center; 570-941-7680) – Private support and guidance for students navigating personal challenges that may impact success at the University


## Final Note

The instructor reserve the right to modify this syllabus; students will immediately be notified of any such changes and an updated syllabus will be made available to the class via the course learning management system.


